Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-10 code/analysis.Rmd
Done with AGU poster until I hear from Laurel

save_plot("../pics/ece_plot.png",plotece, dpi = 600)

@@

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(phi[c]), color = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent) +
  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi[c]^-1.41")

@@

```{r message=FALSE, warning=FALSE, eval=FALSE}

@@

@@

```{r message=FALSE, warning=FALSE, eval=FALSE}

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(phi[c])) +
  ylab(expression(beta[log(Re[c])]))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(Re[c])) +
  ylab(expression(beta[log(phi[c])]))

>>>>

save_plot("../pics/ece_plot.png",plotece, dpi = 600, base_asp = 1.75)

@@

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent) +
  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi[c]^-1.41")

@@

```{r message=FALSE, warning=FALSE}

@@

set.seed(42)

@@

```{r message=FALSE, warning=FALSE}

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c("*",NA,"*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(paste("Collector Solid Volume Fraction (",phi[c]," )"))) +
  ylab(expression(beta[log(Re[c])]))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  geom_hline(yintercept = 0, lty = 2) +
  theme_bw() +
  geom_text(aes(y = avg + 1.96*sd + 1, label = c(NA,"*","*")), fontface = "bold", size = 5) +
  ylim(-3,1.5) +
  xlab(expression(paste("Collector Reynolds Number (",Re[c]," )"))) +
  ylab(expression(beta[log(phi[c])]))
